What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-26 android-stacks.tex
small changes on sections 2 and dicussions

Android is an open source platform for mobile devices based on Linux kernel,
which also contains by a core Java library, a set of libraries third-party libraries (e.g.  SQLite),
the Dalvik runtime environment, and the Application Framework (which provides higher-level services to the applications
running on the platform).

@@

@@

The goal of this study was to extract nformation available on exception stack 
traces embedded on issues reported on Android projects, looking for the common characteristics of
those issues and investigating whether they could reveal common defficiencies
on the exception handling code of both the applications and the underlaying 
 framework.

We choose Android apps because it is the only top platform that is open-source,
and due to its increasing popularity it xxxx.

Our study focused on free apps, since the information needed to perform our study
cannot be retrieved from commercial apps because their issue reports and their
source code is not publicly available. The Android open-source apps were also 
target of other research studies [fse2013][ahimed].

@@

  \item[RQ1] \noindent\emph{What are the common characteristics of exception stack traces reported on issues?} What are the main causes of crashes reported on issues? (more explicit?)

  \item[RQ2] \noindent\emph{What patterns of exception (mis)-use related to exception types and propagation emerge from the exception stack trace analysis?}

@@

The exceptions available on exception stack traces are not limited to the exceptions 
expliciltly thrown by the Java developer but also include
the exceptions implicitly thrown by the JVM due to programming errors (e.g., out-of-bounds array index, division-by-zero, 
access to a null reference) or resource limitation (e.g., OutOfMemoryError).

@@

@@

>>>>

Android is an open source platform for mobile devices based on Linux kernel,
which also contains  a core Java library, a set of libraries third-party libraries (e.g.  SQLite),
the Dalvik runtime environment, and the Application Framework (which provides higher-level services to the applications
running on the platform).

@@

<AVALIAR MOVER ESTE STACK TRACES PARA UMA FIGURA QUE MOSTR COMO ELE É QUEBRADO...
PELO EXCEPTION MINER E AS INFORMAÇÕES VAO PARA O BANCO...>

@@

This study focus on the analysis of crash information (related to uncaught exceptions) of a family of Android applications
aiming at  extracting their common characteristics and looking for similar vulnerabilities on applications and underlaying platform.

In Java when an application crashes dut to an uncaught exception ... 
Exception Stach trace is usually (procurar por artigo).

Falar da assumption que stacj trá relacionada a crash?

The goal of this study was to extract exception stack 
traces embedded on issues of Android projects (hosted in GitHub and GoogleCode), looking for the 
common characteristics of such stack-trace and investigating whether
 they could reveal common defficiencies on the exception handling code of both the applications and the underlaying 
 framework.

Our study focused on open-source apps, since the information needed to perform our study
cannot be retrieved from commercial apps, whose issue reports and 
source code are not publicly available. The Android open-source apps were also 
target of other research studies [fse2013][ahimed].

@@

  \item[RQ1] \noindent\emph{What are the common characteristics of exception stack traces reported on issues?} Some of the common characteristics to be investigated are the 
 main causes reported on exception stack traces, the elements responsible for signaling such exceptions.

  \item[RQ2] \noindent\emph{What patterns of exception (mis)-use related to exception types and propagation emerge from the exception stack trace analysis? Based on a set of best practices
compiled in this study, looked for characteristics on stack traces that could pinpoint to practices that were not being obeyed.}

@@

@@

INSERIR EM ALGUM PONTO DO TEXTO:
The exceptions available on exception stack traces are not limited to the exceptions 
expliciltly thrown by the Java developer but also include
the exceptions implicitly thrown by the JVM due to programming errors (e.g., out-of-bounds array index, division-by-zero, 
access to a null reference) or resource limitation (e.g., OutOfMemoryError).

@@

\subsection{Inversion of Control and Exception Handling}
- Falar de Pytolomy e Ridresh rajan... desafios ja apontados....
